Jeff Goldsmith

### 2018-07-06 index.Rmd
replace icon; other minor rebuild updates

<link rel="stylesheet" href="styles.css" type="text/css">
<link rel="stylesheet" href="academicons/css/academicons.min.css"/>

>>>>

<link rel="stylesheet" href="styles.css" type="text/css">
<link rel="stylesheet" href="academicons/css/academicons.min.css"/>
<link rel="apple-touch-icon" href="/images/JG_transparent.png" >
